EEG characterization and classification based on Histogram of Gradients of Signal Plots

### 2017-09-17 article.tex
Minor changes

This article unfolds as follows: in Section \ref{Feature} the Feature Extraction based on Histogram of Gradients of the Signal Plot method is explained: section \ref{Preprocessing} and \ref{Pipeline} describe the processing pipeline.  Section \ref{Plot}  clarifies how the image of the signal plot is constructed whereas Section \ref{SIFT}  describes in detail the feature extraction procedure.  Section \ref{Classification}  presents the classification algorithm based on Naive Bayes Near Neighbor  and the final Section shows results and discussion where we expose our remarks, conclusions and future work.

>>>>

This article unfolds as follows: in Section \ref{Feature} the Feature Extraction based on Histogram of Gradients of the Signal Plot method is explained. Section \ref{Preprocessing} and \ref{Pipeline} describe the processing pipeline.  Section \ref{Plot}  clarifies how the image of the signal plot is constructed whereas Section \ref{SIFT}  describes in detail the feature extraction procedure.  Section \ref{Classification}  presents the classification algorithm based on Naive Bayes Near Neighbor  and the final Section shows results and discussion where we expose our remarks, conclusions and future work.
